Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-09-13 RR_manuscript/Draft_RR.Rmd
♻️ - edit RR; include new shrinkage plot

msa_sd <- msa_mean_sd_df %>% group_by(outcome, temporal_window) %>%
  summarise(
    sd_min = min(sd),
    sd_med = mean(sd),
    sd_max = max(sd),
    .groups = "drop"
  )

msa_sd_
```

@@

```{r plot-meta1, echo = FALSE, fig.cap="(ref:metaPlot1)", out.width="100%"}
knitr::include_graphics(here::here("./figs/meta_plot1_nest.png"), error = FALSE)
```

>>>>

msa_sd <- msa_mean_sd_df %>% group_by(outcome, temporal_window) %>%
  summarise(
    sd_min = min(sd),
    # sd_mean = mean(sd),
    sd_max = max(sd),
    .groups = "drop"
  )

msa_sd_sd_lo <- msa_sd %>%
  mutate(
    across(starts_with("sd_"), ~.x * meta_sd_clo),
    ci = "low"
  ) %>%
  pivot_longer(sd_min:sd_max, names_to = "sd")
msa_sd_sd_hi <- msa_sd %>%
  mutate(
    across(starts_with("sd_"), ~.x * meta_sd_chi),
    ci = "high"
  ) %>%
  pivot_longer(sd_min:sd_max, names_to = "sd")

msa_sd_sd <- bind_rows(msa_sd_sd_lo, msa_sd_sd_hi)
```

@@

```{r plot-meta1, echo = FALSE, fig.cap="(ref:metaPlot1)", out.width="100%"}
knitr::include_graphics(here::here("./figs/meta_plot1_shrinkage.png"), error = FALSE)
```
